Solutions to Integer Programming from Quantum Annealing

### 2020-09-12 paper/main.tex
ref fig for sim check
clean up plots

\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
	\author{Chih-Chieh~Chen (\begin{CJK*}{UTF8}{bsmi}\mbox{陳志傑}\end{CJK*})}
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\author{Christopher K\"orber}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\author{Jim~Ostrowski}
\affiliation{University of Tennessee}

@@

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
\label{sec:methods:simulation_details}
%----------------------------------------------------------------------------------------
To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
In this case the analytical solution can be obtained for the wave function oscillation.
The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation. The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
{\color{red} Are you suppose to reference Fig. 7 here?}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./figures/check.png}
	\caption{check}
	\label{fig:check}
\end{figure}

>>>>

\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
	\author{Chih-Chieh~Chen }
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\author{Christopher K\"orber}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\author{Jim~Ostrowski}
\affiliation{University of Tennessee}

@@

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
\label{sec:methods:simulation_details}
%----------------------------------------------------------------------------------------
To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
In this case the analytical solution can be obtained for the wave function oscillation.
The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation. The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction. The oscillation is depicted in Figure \ref{figcheck}, where the simulation matches the expected theoretical behavior.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
	\caption{check}
	\label{figcheck}
\end{figure}
